### 2015-04-16 docs/ms.Rmd
Made a minor correction on calculation of teh number of studies using colourmetric variables. Excluded some in prior analysis because studies categorized as multiple were not included in the calculation. Fixed

Our literature survey suggests there is surprising inconsistency and incompleteness in commonly reported methodological details (Fig. 1). Most studies (n = `r specs+both`) used a spectrometer to measure colour, yet integration times (`r round(propSpec_fin["prop_int_time"], digits = 0)`%), and probe-sample geometry (`r round(propSpec_fin["prop_spec_angle"], digits = 0)`%) and distance (`r round(propSpec_fin["prop_spec_dist"], digits = 0)`%) were often not reported. Among studies that used photography (n = `r cam+both`), `r round(propCam_fin["prop_specpix_avg"], digits = 0)`% detailed the number of pixels averaged, though camera models were more frequently reported (`r round(camModel, digits = 0)`%). Light sources were detailed in `r round(propSpec_fin["prop_light_source"], digits = 0)`% and `r round(propCam_fin["prop_light_source"], digits = 0)`% of spectrometer- and camera-based studies, respectively. With regard to data analysis, of the `r analysisType[1]` studies that calculated colourimeteric variables, `r round(col_def, digits = 0)`% specifically defined their measure of brightness, hue and/or chroma. The receptor-noise limited model (Vorobyev et al. 1998) was commonly used among studies with visual modelling (`r vismod_type[3]` of `r sum(vismod_type)`), though there was considerable variation in the detailing of the type of receptor noise used (`r round(propSpec_fin["prop_vis_mod_noise_type"], digits = 0)`% reported), the type of quantum catch used (`r round(propSpec_fin["prop_vis_mod_qcatch"], digits = 0)`%), or whether photoreceptor adaptation (`r round(propSpec_fin["prop_vis_mod_adapt"], digits = 0)`%) was modelled. In contrast, details of the species’ visual system being modelled (`r round(propSpec_fin["prop_vis_mod_sp"], digits = 0)`%), the background used (`r round(propSpec_fin["prop_vis_mod_bkg"], digits = 0)`%), and the modelled illuminant (`r round(propSpec_fin["prop_irrad_type"], digits = 0)`%) were more commonly reported.

>>>>

Our literature survey suggests there is surprising inconsistency and incompleteness in commonly reported methodological details (Fig. 1). Most studies (n = `r specs+both`) used a spectrometer to measure colour, yet integration times (`r round(propSpec_fin["prop_int_time"], digits = 0)`%), and probe-sample geometry (`r round(propSpec_fin["prop_spec_angle"], digits = 0)`%) and distance (`r round(propSpec_fin["prop_spec_dist"], digits = 0)`%) were often not reported. Among studies that used photography (n = `r cam+both`), `r round(propCam_fin["prop_specpix_avg"], digits = 0)`% detailed the number of pixels averaged, though camera models were more frequently reported (`r round(camModel, digits = 0)`%). Light sources were detailed in `r round(propSpec_fin["prop_light_source"], digits = 0)`% and `r round(propCam_fin["prop_light_source"], digits = 0)`% of spectrometer- and camera-based studies, respectively. With regard to data analysis, of the `r colorMet` studies that calculated colourimeteric variables, `r round(col_def, digits = 0)`% specifically defined their measure of brightness, hue and/or chroma. The receptor-noise limited model (Vorobyev et al. 1998) was commonly used among studies with visual modelling (`r vismod_type[3]` of `r sum(vismod_type)`), though there was considerable variation in the detailing of the type of receptor noise used (`r round(propSpec_fin["prop_vis_mod_noise_type"], digits = 0)`% reported), the type of quantum catch used (`r round(propSpec_fin["prop_vis_mod_qcatch"], digits = 0)`%), or whether photoreceptor adaptation (`r round(propSpec_fin["prop_vis_mod_adapt"], digits = 0)`%) was modelled. In contrast, details of the species’ visual system being modelled (`r round(propSpec_fin["prop_vis_mod_sp"], digits = 0)`%), the background used (`r round(propSpec_fin["prop_vis_mod_bkg"], digits = 0)`%), and the modelled illuminant (`r round(propSpec_fin["prop_irrad_type"], digits = 0)`%) were more commonly reported.
